% Copyright (c) 2014,2016,2021 Casper Ti. Vector
% Public domain.

\begin{cabstract}
	%\pkuthssffaq % 中文测试文字
	在当今数字化时代，信息安全的重要性日益凸显，而操作系统的安全性则成为保障用户数据和系统稳定的关键。
	在这样的背景下，Rust 语言以其独特的所有权系统、内存安全等特性而闻名，为操作系统开发带来了新的可能性，
	有效地防范诸如空指针解引用、缓冲区溢出等常见的安全漏洞。
	近期，中关村实验室推出了一款全新的操作系统——Asterinas。
	与传统操作系统不同的是，Asterinas 采用 Rust 语言进行开发，旨在为用户提供更加安全可靠的操作系统环境。
	这一举措体现了对信息安全的高度重视，同时也展示了 Rust 在操作系统开发领域的巨大潜力。
	
	在这一背景下，本研究着眼于 Asterinas 操作系统的文件系统部分，旨在进一步完善其功能。
	我们为 Asterinas 引入 exFAT 文件系统的支持，并对文件系统的页缓存模块增加了数据预取机制。
	此外，我们为新增的 exFAT 文件系统设计了单元测试并运行了集成测试以验证实现的正确性。
	随后，我们针对新增的 exFAT 文件系统和页缓存的数据预取机制，使用 FIO 进行了性能测试，并与 Linux 中的实现进行了比较。
	测试结果表明，使用页缓存时，我们的实现在顺序读写模式上仍然与 Linux 中实现有一定的差距。
	不使用页缓存时，Asterinas 直接与块设备交互的性能要弱于 Linux。
	这个结果说明，页缓存的设计仍有改进的空间，对块设备实现的性能还有待提高，这也将是我们后续继续改进的方向。
	

\end{cabstract}

\ifblind\begin{beabstract}\else\begin{eabstract}\fi
	In today's digital age, the importance of information security is increasingly prominent, 
	with the security of operating systems being a key factor in safeguarding user data and system stability. 
	In this context, Rust language is renowned for its unique ownership system, memory safety, 
	and other features, bringing new possibilities to operating system development and effectively preventing common security vulnerabilities such as null pointer dereferencing and buffer overflows.
	Recently, the Zhongguancun Laboratory has introduced a new operating system called Asterinas. 
	Setting it apart from traditional operating systems, Asterinas is developed using the Rust language, 
	aiming to provide users with a more secure and reliable operating system environment. 
	This initiative demonstrates a high level of emphasis on information security while showcasing the significant potential of Rust in the field of operating system development.
	
	This study focuses on enhancing the implementation of file system component of the Asterinas operating system. 
	We have introduced support for the exFAT file system in Asterinas and 
	added a data prefetching mechanism to the file system's page cache module. 
	Furthermore, we designed unit tests for the newly added exFAT file system and 
	conducted integration tests to verify the correctness of the implementation.	
	Subsequently, we conducted performance tests using FIO on the newly added exFAT file system 
	and page cache data prefetching mechanism, comparing the results with implementations in Linux.
	The test results indicate that when using the page cache, 
	our implementation still shows some gap compared to Linux in sequential IO mode.
	When not using page caching, Asterinas' performance in directly interacting with block devices is weaker than Linux.
	These results suggest that there is room for improvement in the design of page cache and block device, 
	which will be the focus of future improvements.
\ifblind\end{beabstract}\else\end{eabstract}\fi

% vim:ts=4:sw=4
